BurgerMax Presents: Open Adcess

### 2017-03-01 digital-library.tex
Spelling

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM DL toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

>>>>

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM Digital Library toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

### 2017-03-01 future-work.tex
Spelling

\section{Future Work}
\label{sec:future}
This future work appears in a compilation of great speaches from the ACM
\cite{acm-state}.

@@

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in exchange for their continued appreciation of the
safe practises within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\subsection{Future Work}
A consequence of the invention of time travel \cite{time-travel} and the vanity
of engineers (not scientests) \cite{sci-shirt} is that people keep going
further back in time to give themselves credit for the invention of the time
machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing missadventures during our field trip into the past
can be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.

>>>>

\section{Future Work}
\label{sec:future}
This future work appears in a compilation of great speeches from the ACM
\cite{acm-state}.

@@

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in exchange for their continued appreciation of the
safe practices within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\subsection{Future Work}
A consequence of the invention of time travel \cite{time-travel} and the vanity
of engineers (not scientists) \cite{sci-shirt} is that people keep going
further back in time to give themselves credit for the invention of the time
machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing misadventures during our field trip into the past
can be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.
